A STATISTICAL DISTANCE DERIVED FROM THE KOLMOGOROV-SMIRNOV TEST: SPECIFICATION, REFERENCE MEASURES (BENCHMARKS) AND EXAMPLE USES

### 2017-08-25 emc/article.tex
added Fernando as coauthor

%%-----------------------------------------------EDIT----------------------------------------------
\author
    {\rm \begin{tabular}{l} 
	    \textbf{Renato Fabbri}$^{1}$ - {\textnormal renato.fabbri@gmail.com}\\%
    \textbf{Fernando Gularte De León}$^{2}$ - {\textnormal fernandogularte@gmail.com}\\
	    {\fontsize{11}{0}\selectfont $^{1}$University of São Paulo, Institute of Mathematical and Computer Sciences - São Carlos, SP, Brazil}\vspace*{-0.05cm} \\
    {\fontsize{11}{0}\selectfont $^{2}$Parque Tecnológico Industrial del Cerro - Montevideo, MVD, Uruguay}\vspace*{-0.05cm}\\
  \end{tabular}}
%%----------------------------------------------------------------------------------------------

>>>>

%%-----------------------------------------------EDIT----------------------------------------------
\author
    {\rm \begin{tabular}{l} 
	    \textbf{Renato Fabbri}$^{1}$ - {\textnormal renato.fabbri@gmail.com}\\%
    \textbf{Fernando Gularte De León}$^{2}$ - {\textnormal fernandogularte@gmail.com}\\
	    {\fontsize{11}{0}\selectfont $^{1}$University of São Paulo, Institute of Mathematical and Computer Sciences - São Carlos, SP, Brazil}\vspace*{-0.05cm} \\
	    {\fontsize{11}{0}\selectfont $^{2}$Parque Tecnológico Industrial del Cerro - Montevideo, MO, Uruguay}\vspace*{-0.05cm}\\
  \end{tabular}}
%%----------------------------------------------------------------------------------------------
